---
title: "Assignment 4 - Coordinating Heart Rate"
author: "Riccardo Fusaroli"
date: "November 6, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Analysing Heart Rate and Respiration data

The goal of this assignment is to first familiarize you with heart rate, and respiration data and their preprocessing. The second part explores how to analyze interpersonal coordination of these signals.

These are the questions you need to be able to answer at the end of the assignment (aka that you need to submit as part of the portfolio)

1) How do you preprocess heart rate and respiration data? Describe the process. If any data needs to be excluded, list the excluded data and motivate the exclusion.

2) Do you observe interpersonal coordination in heart rate and respiration? Describe your control baseline, the method used to quantify coordination, and the statistical models used to infer whether coordination was higher than in the baseline. Report the results of the models.

3) Do you observe differences in coordination between conditions? Report the models and results.

4) Is respiration coordination a likely driver of heart rate coordination? Describe how you would test for it. Bonus points if you actually run the tests and report methods and results.

N.B. to give you a bit more data I included data from last year (Study1) and from your class (Study2). Note that synchronouns and turn-taking are the same across both studies, but the third condition is different: last year it was self-paced joint reading; this year it was the tv-series conversation. So you might want to exclude the self-paced reading (but, up to you!)

## Step by step suggestions to solve the assignment

### Exploring physiological signals

- Choose one pair (one pair, three conditions)
- Load the logs
- Produce a plot of the participants' respiration signal and a different one of the participants' HR signal (for inspecting whether the data is usable)
  N.B: remember the slides: artifacts, downsampling, scaling.
  N.B. The gridExtra::grid.arrange() function allows you to display the plots side by side. E.g. grid.arrange(plot1, plot2, plot3, ncol=3)
- Can you eye-ball which condition if any displays more physiological coordination?

- Run crqa on heart rate and respiration data (find parameters, run crqa)
- Does this tell you more than just eyeballing the plots?

```{r}
# Some packgages
pacman::p_load(knitr,lme4,caret,e1071,pROC,dplyr,gridExtra,pacman,crqa,stringr)

# Read in data from 3 files to compare them on the plots
data1 = read.csv("./CleanData/Study2_G10_T1_Conversation.csv")
data2 = read.csv("./CleanData/Study2_G10_T2_TurnTaking.csv")
data3 = read.csv("./CleanData/Study2_G10_T3_Synchronous.csv")

# Make the plots for the data
plot1 = ggplot(data1, aes(time, Resp1)) + 
  geom_line() +
  geom_line(aes(time, Resp2),color="red")

plot2 = ggplot(data2, aes(time, Resp1)) + 
  geom_line() + 
  geom_line(aes(time, Resp2), color="red")

plot3 = ggplot(data3, aes(time, Resp1)) + 
  geom_line() +
  geom_line(aes(time, Resp2), color="red")

# Plot the respiration data of the 3 files together
gridExtra::grid.arrange(plot1,plot2,plot3)

# Make plots for heart rate data
plot12 = ggplot(data1, aes(time, HR1)) + 
  geom_line() +
  geom_line(aes(time, HR2),color="red")

plot22 = ggplot(data2, aes(time, HR1)) + 
  geom_line() + 
  geom_line(aes(time, HR2), color="red")

plot32 = ggplot(data3, aes(time, HR1)) + 
  geom_line() +
  geom_line(aes(time, HR2), color="red")

# Plot the respiration data of the 3 files together
gridExtra::grid.arrange(plot12,plot22,plot32)

```

The respiration data in the 1st two of the chosen files falls flat for one of the participants. For further analysis I will use the third file because respiration data for both participants are not flat.

```{r}
# Downsample so R could handle
pacman::p_load(groupdata2)

#CRQA works for this file
data3 = read.csv("./CleanData/Study2_G8_T3_Conversation.csv")

d1 = data3 %>%
  group(n = 100, method = 'greedy') %>%
  dplyr::summarise(
    time= mean(time,na.rm=T),
    HR1 = mean(HR1,na.rm=T),
    HR2 = mean(HR2,na.rm=T),
    Resp1 = mean(Resp1,na.rm=T),
    Resp2 = mean(Resp2,na.rm=T))

# Remove artifacts - points where signal was lost (low drops in HR data for example), remove them before rescaling
## Artifact removal function
removeOuts <- function(ts,threshold){
  ts[ts > (mean(ts,na.rm=T) +
             (threshold*sd(ts,na.rm=T))) |  
       ts < (mean(ts,na.rm=T) -
             (threshold*sd(ts,na.rm=T)))] = 
    mean(ts,na.rm=T)   
  return(ts)}
# Set threshold
threshold = 2.5

d1$HR1=removeOuts(d1$HR1,threshold)
d1$HR2=removeOuts(d1$HR2,threshold)
d1$Resp1=removeOuts(d1$Resp1,threshold)
d1$Resp2=removeOuts(d1$Resp2,threshold)

# Rescaling the data so that the baseline for different people would be the same and variation comparable
d1$Resp1 = scale(d1$Resp1)
d1$Resp2 = scale(d1$Resp2)  
d1$HR1 = scale(d1$HR1)
d1$HR2 = scale(d1$HR2)
```


```{r}
# Run crqa
## Get parameters
par = list(lgM =  30, steps = seq(1, 6, 1),  radiusspan = 100,  radiussample = 100, normalize = 0,  rescale = 0,  mindiagline = 2,  minvertline = 2,  tw = 0,  whiteline = FALSE,  recpt = FALSE,  fnnpercent = 10,  typeami = "mindip")
ans = optimizeParam(d1$HR1, d1$HR2, par, min.rec= 2, max.rec= 8)
## CRQA analysis
crqa_one = crqa (d1$HR1, d1$HR2, delay=ans$delay, embed=ans$emddim, radius=ans$radius, normalize=0, rescale=0, mindiagline = 2, minvertline = 2)

## Plot
RP = crqa_one$RP
RP = matrix(as.numeric(RP), nrow = ncol(RP))
cols = c("white","blue4")
image(RP, xlab = "", ylab = "", col = cols)
```

### Systematically pre-process the data
- Loop through all the files (either with a loop or with a function), check which files should be excluded, if any, and save the pre-processed time-series. Tip: plot and visually inspect the data to figure out which should be excluded.

```{r}
# Make sure to visualize the plots to know what to exclude
# Visualize data loop
## Seems like flatlines have a mean thats close to -10 and nonflats have it close to 0, remove files where the mean of resp1 OR resp2 is close to -10
pacman::p_load(groupdata2)

```

```{r}
### LOOP TO PREPROCESS FILES ###

# List files
fileNames = list.files(path = "./CleanData", pattern = "Study", full.names = T)

# The loop
for (i in fileNames){
  # Read in file
  temp = read.csv(i)
  
  # If statement that tries to exclude the flat respirations
  if((mean(temp$Resp1, na.rm = TRUE) >= -7) & (mean(temp$Resp2, na.rm = TRUE) >= -7)){
  # If isn't flat then:
    # Downsample
    temp = temp %>%
        groupdata2::group(n = 100, method = 'greedy') %>%
        dplyr::summarise(
          time= mean(time,na.rm=T),
          HR1 = mean(HR1,na.rm=T),
          HR2 = mean(HR2,na.rm=T),
          Resp1 = mean(Resp1,na.rm=T),
          Resp2 = mean(Resp2,na.rm=T))
    
    # Remove artifacts
    temp$HR1=removeOuts(temp$HR1,threshold)
    temp$HR2=removeOuts(temp$HR2,threshold)
    temp$Resp1=removeOuts(temp$Resp1,threshold)
    temp$Resp2=removeOuts(temp$Resp2,threshold)
    
    # Rescaling
    temp$Resp1 = scale(temp$Resp1)
    temp$Resp2 = scale(temp$Resp2)  
    temp$HR1 = scale(temp$HR1)
    temp$HR2 = scale(temp$HR2)
    
  m = gsub("./CleanData/Study", "./WOExcluded/P_Study", i)
  write.csv(temp, file = m)

  } else {
  # Print the files that were excluded
  print(i)
  }
}


```
Excluded
[1] "./CleanData/Study1_G1_T1_Synchronous.csv"
[1] "./CleanData/Study1_G1_T2_TurnTaking.csv"
[1] "./CleanData/Study1_G2_T1_TurnTaking.csv"
[1] "./CleanData/Study1_G2_T2_Synchronous.csv"

```{r}
# Make plots for preprocessed files
# Read in data from 3 files to compare them on the plots
data1 = read.csv("./Processed/P_Study2_G10_T1_Conversation.csv")
data2 = read.csv("./Processed/P_Study2_G10_T2_TurnTaking.csv")
data3 = read.csv("./Processed/P_Study2_G10_T3_Synchronous.csv")

# Make the plots for the data
plot1 = ggplot(data1, aes(time, Resp1)) + 
  geom_line() +
  geom_line(aes(time, Resp2),color="red")

plot2 = ggplot(data2, aes(time, Resp1)) + 
  geom_line() + 
  geom_line(aes(time, Resp2), color="red")

plot3 = ggplot(data3, aes(time, Resp1)) + 
  geom_line() +
  geom_line(aes(time, Resp2), color="red")

# Plot the respiration data of the 3 files together
gridExtra::grid.arrange(plot1,plot2,plot3)

# Make plots for heart rate data
plot12 = ggplot(data1, aes(time, HR1)) + 
  geom_line() +
  geom_line(aes(time, HR2),color="red")

plot22 = ggplot(data2, aes(time, HR1)) + 
  geom_line() + 
  geom_line(aes(time, HR2), color="red")

plot32 = ggplot(data3, aes(time, HR1)) + 
  geom_line() +
  geom_line(aes(time, HR2), color="red")

# Plot the respiration data of the 3 files together
gridExtra::grid.arrange(plot12,plot22,plot32)

```


```{r}
# Function donated by the generous programming angels that finds the optimal parameters for files that have them, and makes a list of NA's for those that haven't
fitCrqa <- function(ts1,ts2){
  
  par = list(lgM = 30, steps = seq(1, 6, 1), radiusspan = 100, radiussample = 100, normalize = 0, rescale = 0, mindiagline = 2, minvertline = 2, tw = 0, whiteline = FALSE, recpt = FALSE, fnnpercent = 10, typeami = "mindip")
  
  Pars = try(optimizeParam(ts1, ts2, par, min.rec = 2, max.rec = 8))
  
  if (length(Pars)>1){
    Results=crqa(ts1, ts2, delay=Pars$delay, embed=Pars$emddim, radius=Pars$radius, normalize=0, rescale=0, mindiagline = 2, minvertline = 2)
  } else {
    Results=NULL
    Pars=NULL
    Pars$delay=NA
    Pars$emddim=NA
    Pars$radius=NA
    Results$RR=NA
    Results$DET=NA
    Results$maxL=NA
    Results$L=NA
    Results$ENTR=NA
    Results$LAM=NA
    Results$TT=NA
  }
  
  df=data.frame(Delay=Pars$delay,Embed=Pars$emddim,Radius=Pars$radius,RR=Results$RR,DET=Results$DET,LMAX=Results$maxL,L=Results$L,ENTR=Results$ENTR,LAM=Results$LAM,TT=Results$TT)
  
  print(df)
  
}

# Create the data frame
Resp_Parameters = as.data.frame(NULL)
# For loop to create a dataframe that has the values of CRQA parameters in it

# Get the files that are preprocessed
P_fileNames = list.files(path = "./Processed", pattern = "P_Study", full.names = T)

for (i in P_fileNames){
  # Read in file
  temp = read.csv(i)
  
  fitted = fitCrqa(temp$Resp1, temp$Resp2)
  
  # Add name of row
  add_row = data.frame(Name = i)

  # Bind final dataframe with all results
  #Resp_Parameters = rbind(Resp_Parameters, add_row)
  Resp_Parameters = rbind(Resp_Parameters, fitted)
}

# Write the table out just in case
write.csv(Resp_Parameters, "Resp_Parameters")

# Same thing on heartrate
# Create the data frame
HR_Parameters = as.data.frame(NULL)
# For loop to create a dataframe that has the values of CRQA parameters in it

# Get the files that are preprocessed
P_fileNames = list.files(path = "./Processed", pattern = "P_Study", full.names = T)

for (i in P_fileNames){
  # Read in file
  temp = read.csv(i)
  
  fitted = fitCrqa(temp$HR1, temp$HR2)
  
  # Add name of row
  add_row = data.frame(Name = i)

  # Bind final dataframe with all results
  #Resp_Parameters = rbind(Resp_Parameters, add_row)
  HR_Parameters = rbind(HR_Parameters, fitted)
}

# Write the table out just in case
write.csv(HR_Parameters, "HR_Parameters")
```

- Run crqa on all the pre-processed time-series and save the output (don't forget to add columns with study, group, condition and trial). Tip: remember to first assess optimal parameters (dimensions, delay, radius) across all timeseries. Tip: it will often fail, just take whatever parameters you get, select optimal across timeseries parameters and run crqa on all timeseries with those. Tip: double check the rr. When I ran the loop, I got very low rr, so I adjusted the radius until the average of rr across all pairs was approx. 4%.

```{r}
# Find some good parameters
median(Resp_Parameters$RR, na.rm=T) # seems fine
median(Resp_Parameters$Delay, na.rm=T) # 18
median(Resp_Parameters$Embed, na.rm=T) # 2
median(Resp_Parameters$Radius, na.rm=T) # 0.3778026

median(HR_Parameters$RR, na.rm=T) # seems fine
median(HR_Parameters$Delay, na.rm=T) # 0
median(HR_Parameters$Embed, na.rm=T) # 17
median(HR_Parameters$Radius, na.rm=T) # 0.3761792

# Change the parameters
par = list(lgM = 30, steps = seq(1, 6, 1), radiusspan = 100, radiussample = 100, normalize = 0, rescale = 0, mindiagline = 2, minvertline = 2, tw = 0, whiteline = FALSE, recpt = FALSE, fnnpercent = 10, typeami = "mindip")
Resp_ans = optimizeParam(d3$Resp1, d3$Resp2, par, min.rec= 2, max.rec= 8)
HR_ans = optimizeParam(d3$HR1, d3$HR2, par, min.rec= 2, max.rec= 8)

Resp_ans$radius = median(Resp_Parameters$Radius, na.rm=T)
Resp_ans$emddim = 2
Resp_ans$delay = 18

HR_ans$radius = median(HR_Parameters$Radius, na.rm=T) + 1.2
HR_ans$emddim = 17
HR_ans$delay = 0

# Loop through files, get CRQA results
## Removed the self-paced files manually
## Get the files that are preprocessed
P_fileNames = list.files(path = "./Processed", pattern = "P_Study", full.names = T)

# Change the function to have parameter values
HR_fitCrqa <- function(ts1,ts2){
  
  par = list(lgM = 30, steps = seq(1, 6, 1), radiusspan = 100, radiussample = 100, normalize = 0, rescale = 0, mindiagline = 2, minvertline = 2, tw = 0, whiteline = FALSE, recpt = FALSE, fnnpercent = 10, typeami = "mindip")
  
  HR_ans = HR_ans
  
  Results = try(crqa(ts1, ts2, delay=HR_ans$delay, embed=HR_ans$emddim, radius=HR_ans$radius, normalize=0, rescale=0, mindiagline = 2, minvertline = 2))
  
  if (length(Results)<2){
    Results=NULL
    Results$HR_RR=NA
    Results$HR_DET=NA
    Results$HR_maxL=NA
    Results$HR_L=NA
    Results$HR_ENTR=NA
    Results$HR_LAM=NA
    Results$HR_TT=NA
    
  } else {
    Results=Results
    Results$HR_RR=Results$RR
    Results$HR_DET=Results$DET
    Results$HR_maxL=Results$maxL
    Results$HR_L=Results$L
    Results$HR_ENTR=Results$ENTR
    Results$HR_LAM=Results$LAM
    Results$HR_TT=Results$TT
  }
  
  df=data.frame(HR_RR=Results$HR_RR,HR_DET=Results$HR_DET,HR_LMAX=Results$HR_maxL,HR_L=Results$HR_L,HR_ENTR=Results$HR_ENTR,HR_LAM=Results$HR_LAM,HR_TT=Results$HR_TT)
  
  print(df)
}

#HR_fitCrqa(d3$HR1, d3$HR2)

Resp_fitCrqa <- function(ts1,ts2){
  
  par = list(lgM = 30, steps = seq(1, 6, 1), radiusspan = 100, radiussample = 100, normalize = 0, rescale = 0, mindiagline = 2, minvertline = 2, tw = 0, whiteline = FALSE, recpt = FALSE, fnnpercent = 10, typeami = "mindip")
  Resp_ans = Resp_ans
  
  Results=try(crqa(ts1, ts2, delay=Resp_ans$delay, embed=Resp_ans$emddim, radius=Resp_ans$radius, normalize=0, rescale=0, mindiagline = 2, minvertline = 2))

  if (length(Results)<2){
    Results=NULL
    Results$Resp_RR=NA
    Results$Resp_DET=NA
    Results$Resp_maxL=NA
    Results$Resp_L=NA
    Results$Resp_ENTR=NA
    Results$Resp_LAM=NA
    Results$Resp_TT=NA
    
  } else {
    
    Results=Results
    Results$Resp_RR=Results$RR
    Results$Resp_DET=Results$DET
    Results$Resp_maxL=Results$maxL
    Results$Resp_L=Results$L
    Results$Resp_ENTR=Results$ENTR
    Results$Resp_LAM=Results$LAM
    Results$Resp_TT=Results$TT
  }
  
  df=data.frame(Resp_RR=Results$Resp_RR,Resp_DET=Results$Resp_DET,Resp_LMAX=Results$Resp_maxL,Resp_L=Results$Resp_L,Resp_ENTR=Results$Resp_ENTR,Resp_LAM=Results$Resp_LAM,Resp_TT=Results$Resp_TT)
  
  print(df)
}

#b = Resp_fitCrqa(d2$Resp1, d2$Resp2)
```

### Creating controls: shuffled controls
 - loop through all pairs and conditions
 - shuffle the timeseries (take a timeseries and rearrange its values in a random order). Tip check the sample() function
 - run crqa and save the output. NB. which delay, embed, radius parameters should you use?
 - statistically compare the crqa indexes in real and shuffled pairs

```{r}
# CREATE SHUFFLED PAIRS
C_fileNames = list.files(path = "./Processed", pattern = "P_Study", full.names = T)

# Loop it
for (i in C_fileNames) {
  #Put the path together with the filename
  #dest = paste("P_", i, sep="")
  #Read it
  d_t <- read.csv(i, header = T)
  
  #Randomize the order of datapoints
  d_t$HR1x = sample(d_t$HR1, length(d_t$HR1))
  d_t$HR1 = d_t$HR1x
  d_t$HR2x = sample(d_t$HR2, length(d_t$HR2))
  d_t$HR2 = d_t$HR2x
  d_t$Resp1x = sample(d_t$Resp1, length(d_t$Resp1))
  d_t$Resp1 = d_t$Resp1x
  d_t$Resp2x = sample(d_t$Resp2, length(d_t$Resp2))
  d_t$Resp2 = d_t$Resp2x
  
  #create new files

  m = gsub("./Processed/P_Study", "./Shuffled/Shuff_Study", i)
  write.csv(temp, file = m)
}

```

### TRICKY! Creating controls: surrogate pair controls
 - Per each real pair, identify at least one surrogate pair (matching one of the participants, with somebody doing the same task, but in a different pair). Tip: Celine will share a commented script
 - Run crqa on all the surrogate pairs and save the output. NB. which delay, embed, radius parameters should you use?
 - Test whether crqa shows a difference between real and surrogate pairs

```{r}
##done in the file called surrogate-pairs.Rmd
```


```{r}
### Make the 1st dataframe WITH REAL PAIRS ###

CRQA_results1 = as.data.frame(NULL)
Study = NULL
Group = NULL
Trial = NULL
Condition = NULL
#Type = NULL
n = 1

P_fileNames = list.files(path = "./Processed", pattern = "P_Study", full.names = T)
# The loop
for (i in P_fileNames){
  # Read in file
  temp = read.csv(i)
  
  # Get the names
  Study[n] = str_extract(i, "Study+\\d+") %>%   
      str_extract("\\d+")
  Group[n] = str_extract(i, "G+\\d+") %>%   
      str_extract("\\d+")
  Trial[n] = str_extract(i, "T+\\d+") %>%   
      str_extract("\\d+")
  Condition[n] = gsub(".*[_]([^.]+)[.].*", "\\1", i)
  
  #Name[n] = cbind(Study, Group, Trial, Condition)
  
  HR_fitted = HR_fitCrqa(temp$HR1, temp$HR2)
  Resp_fitted = Resp_fitCrqa(temp$Resp1, temp$Resp2)
  Type = "Real"
  
  together = cbind(Resp_fitted, HR_fitted, Type)

  # Bind final dataframe with all results
  CRQA_results1 = rbind(CRQA_results1, together)
  n = n+1
  
  print(i)
}

Final = cbind(Study, Group, Trial, Condition, CRQA_results1)

### WITH SURROGATE PAIRS ###

CRQA_results2 = as.data.frame(NULL)
Study = NULL
Group = NULL
Trial = NULL
Condition = NULL
#Type = NULL
n = 1

P_fileNames = list.files(path = "./surrogate", pattern = "Study", full.names = T)
# The loop
for (i in P_fileNames){
  # Read in file
  temp = read.csv(i)
  
  # Get the names
  Study[n] = str_extract(i, "Study+\\d+") %>%   
      str_extract("\\d+")
  Group[n] = str_extract(i, "Group+\\d+&\\d")
  Trial[n] = str_extract(i, "T+\\d+") %>%   
      str_extract("\\d+")
  Condition[n] = gsub(".*[_]([^.]+)[.].*", "\\1", i)
  
  HR_fitted = HR_fitCrqa(temp$HR1, temp$HR2)
  Resp_fitted = Resp_fitCrqa(temp$Resp1, temp$Resp2)
  Type = "Surrogate"
  
  together = cbind(Resp_fitted, HR_fitted, Type)

  # Bind final dataframe with all results
  CRQA_results2 = rbind(CRQA_results2, together)
  n = n+1
  
  print(i)
}

Final2 = cbind(Study, Group, Trial, Condition, CRQA_results2)


### For controls ###

CRQA_results3 = as.data.frame(NULL)
Study = NULL
Group = NULL
Trial = NULL
Condition = NULL
#Type = NULL
n = 1

P_fileNames = list.files(path = "./Shuffled", pattern = "Shuff", full.names = T)
# The loop
for (i in P_fileNames){
  # Read in file
  temp = read.csv(i)
  
  # Get the names
  Study[n] = str_extract(i, "Study+\\d+") %>%   
      str_extract("\\d+")
  Group[n] = str_extract(i, "G+\\d+") %>%   
      str_extract("\\d+")
  Trial[n] = str_extract(i, "T+\\d+") %>%   
      str_extract("\\d+")
  Condition[n] = gsub(".*[_]([^.]+)[.].*", "\\1", i)
  
  HR_fitted = HR_fitCrqa(temp$HR1, temp$HR2)
  Resp_fitted = Resp_fitCrqa(temp$Resp1, temp$Resp2)
  Type = "Shuffled"
  
  together = cbind(Resp_fitted, HR_fitted, Type)

  # Bind final dataframe with all results
  CRQA_results3 = rbind(CRQA_results3, together)
  n = n+1
  
  print(i)
}

Final3 = cbind(Study, Group, Trial, Condition, CRQA_results3)
```

```{r}
# Bind into one huge dataframe
FINAL = rbind(Final, Final2, Final3)

# Write file out just in case
write.csv(FINAL, "Final_dataset.csv")
```

### Testing effects of conditions
 - make a (probably underpowered) mixed model testing effects of the different conditions on heart rate and respiration coordination
 - N.B: would it make sense to include surrogate pairs? and if so how? what would that tell you?
 
 
```{r}
# Visualize some things
#For type
g1 =ggplot(FINAL, aes(Type, Resp_RR)) +
  geom_boxplot()
g2 =ggplot(FINAL, aes(Type, Resp_DET)) +
  geom_boxplot()
g3 =ggplot(FINAL, aes(Type, Resp_LMAX)) +
  geom_boxplot()
g4 =ggplot(FINAL, aes(Type, Resp_L)) +
  geom_boxplot()
g5 =ggplot(FINAL, aes(Type, Resp_ENTR)) +
  geom_boxplot()
g6 =ggplot(FINAL, aes(Type, Resp_LAM)) +
  geom_boxplot()
g7 =ggplot(FINAL, aes(Type, Resp_TT)) +
  geom_boxplot()
grid.arrange(g1,g2,g3,g4,g5,g6,g7)

g1 =ggplot(FINAL, aes(Type, HR_RR)) +
  geom_boxplot()
g2 =ggplot(FINAL, aes(Type, HR_DET)) +
  geom_boxplot()
g3 =ggplot(FINAL, aes(Type, HR_LMAX)) +
  geom_boxplot()
g4 =ggplot(FINAL, aes(Type, HR_L)) +
  geom_boxplot()
g5 =ggplot(FINAL, aes(Type, HR_ENTR)) +
  geom_boxplot()
g6 =ggplot(FINAL, aes(Type, HR_LAM)) +
  geom_boxplot()
g7 =ggplot(FINAL, aes(Type, HR_TT)) +
  geom_boxplot()
grid.arrange(g1,g2,g3,g4,g5,g6,g7)


#For condition
g1 =ggplot(FINAL, aes(Condition, Resp_RR)) +
  geom_boxplot()
g2 =ggplot(FINAL, aes(Condition, Resp_DET)) +
  geom_boxplot()
g3 =ggplot(FINAL, aes(Condition, Resp_LMAX)) +
  geom_boxplot()
g4 =ggplot(FINAL, aes(Condition, Resp_L)) +
  geom_boxplot()
g5 =ggplot(FINAL, aes(Condition, Resp_ENTR)) +
  geom_boxplot()
g6 =ggplot(FINAL, aes(Condition, Resp_LAM)) +
  geom_boxplot()
g7 =ggplot(FINAL, aes(Condition, Resp_TT)) +
  geom_boxplot()
grid.arrange(g1,g2,g3,g4,g5,g6,g7)

g1 =ggplot(FINAL, aes(Condition, HR_RR)) +
  geom_boxplot()
g2 =ggplot(FINAL, aes(Condition, HR_DET)) +
  geom_boxplot()
g3 =ggplot(FINAL, aes(Condition, HR_LMAX)) +
  geom_boxplot()
g4 =ggplot(FINAL, aes(Condition, HR_L)) +
  geom_boxplot()
g5 =ggplot(FINAL, aes(Condition, HR_ENTR)) +
  geom_boxplot()
g6 =ggplot(FINAL, aes(Condition, HR_LAM)) +
  geom_boxplot()
g7 =ggplot(FINAL, aes(Condition, HR_TT)) +
  geom_boxplot()
grid.arrange(g1,g2,g3,g4,g5,g6,g7)
```

```{r}
# Loop some results for HR and Resp and see if you can find coordination
# List of all the models that will be tested
goodmodels = c("HR_RR ~ Type + (1|Group)",
               "HR_DET ~ Type + (1|Group)",
               "HR_LMAX ~ Type + (1|Group)",
               "HR_L ~ Type + (1|Group)",
               "HR_ENTR ~ Type + (1|Group)",
               "HR_LAM ~ Type + (1|Group)",
               "HR_TT ~ Type + (1|Group)"
       )

library(caret)
# Loop for ALL MODELS
n = 1
for(i in goodmodels) {
  
  # Make model
  #model2[n] = lmer(model, FINAL)
  
  # Print model output
  print(summary(lmer(i, FINAL)))
  # Print this to see where one model ends and another begins
  print("##############################################")
  
  n = n +1
  
}
```


```{r}
# Loop some results for HR and see if you can find differences in conditions
# List of all the models that will be tested
goodmodels = c("HR_RR ~ Condition + (1|Group)",
               "HR_DET ~ Condition + (1|Group)",
               "HR_LMAX ~ Condition + (1|Group)",
               "HR_L ~ Condition + (1|Group)",
               "HR_ENTR ~ Condition + (1|Group)",
               "HR_LAM ~ Condition + (1|Group)",
               "HR_TT ~ Condition + (1|Group)"
       )

library(caret)
# Loop for ALL MODELS
n = 1
for(i in goodmodels) {
  
  # Make model
  #model2[n] = lmer(model, FINAL)
  
  # Print model output
  print(summary(lmer(i, FINAL)))
  # Print this to see where one model ends and another begins
  print("##############################################")
  
  n = n +1
  
}

#Test interaction
goodmodels = c("HR_RR ~ Condition*Type + (1|Group)",
               "HR_DET ~ Condition*Type + (1|Group)",
               "HR_LMAX ~ Condition*Type + (1|Group)",
               "HR_L ~ Condition*Type + (1|Group)",
               "HR_ENTR ~ Condition*Type + (1|Group)",
               "HR_LAM ~ Condition*Type + (1|Group)",
               "HR_TT ~ Condition*Type + (1|Group)"
       )

library(caret)
# Loop for ALL MODELS
n = 1
for(i in goodmodels) {
  
  # Make model
  #model2[n] = lmer(model, FINAL)
  
  # Print model output
  print(summary(lmer(i, FINAL)))
  # Print this to see where one model ends and another begins
  print("##############################################")
  
  n = n +1
  
}
```

### Effects of respiration coordination on heart rate coordination
 - describe how you would test those.
 - Optional: run the models and report them

